
Tabletop Roleplaying games(TTRPGS) have become increasingly popular in recent years, with shows based around them such as 'Critical Role' raising over 11 million dollars in 45 days in order to create a animated series based on their games. Though popular there is a steep learning curve that requires a decent understanding of the rules which span multiple books and hundreds of pages. \\\\
For this project the goal was to create a social media site that allow for people to share their thoughts and ideas on a forum focused on the topic. TTRPG's such as Dungeons and Dragons have systems built in to allow the players to create their own content with an almost infinite amount of freedom. \\\\
Because of the contradictory nature of this we wanted to make a website that would cater to the free discussion of ideas, while aiding the user in the more complicated process such as making a character which may seem daunting at first with the size of the reading materials.  \\\\
As sessions of these games can often last months or years we wanted to create a database to store information about the sessions on one platform where the history of a group can easily be tracked and not lost, as is often the case with sheets of paper.  \\\\
Our final goal with this project was to create a platform that would allow a person to find a group to play with as despite being popular the topic of TTRPS is not often breached in a standard conversation. Thus this website would allow people to find other players in their area or virtually while aiding in the management and creative process.
