\section{Web Application}
\subsection{Angular}
Angular was initially released in September 2016, with its current stable release (11.2.9) released in April 2021.  Angular is a widely used framework for building single-page client applications using HTML and TypeScript.  With new releasing still being made to date is it a platform that is currently still in use in a wide range of applications, resulting in its use in this project.  The idea behind making a single-page client application was that they are in commonly used and offer a wide range of possibilities with regards to web development. \\

TypeScript is a programming language developed by Microsoft, is a strict syntactical super-set of JavaScript and adds optional static typing to the language.  Meaning that when Typscript is compiled it is converted to the specified version of JavaScript the programmer intends on using.  This results in existing JavaScript programs being valid TypeScript programs.  The importance of this is that JavaScript is one of the most use programming languages in web development.  With these characteristic, Angular is a platform that will mostly likely still be relevant and used for the foreseeable future and thus a valuable asset worth understanding.

\section{Database}
The platform used for this project was Firebase, and was used for storing user data.  This included user information, forums, character and message data.  It was used due to it's NO-SQL, real-time data synchronization something we had not previously worked with.  It was also quite useful as this project does not need a database to store information of millions of users and the use of standard Firebase is free.

\subsection{Firebase}

\section{Cloud Storage}
The provider for the cloud computing platform used in this project is Microsoft Azure.  The use of this platform in this project is to host a virtual machine in which the project is deployed, there is several reasons behind this. Firstly is that users of the application would not as affected by latency due to the location of the local device.  Secondly if the application was stored locally, when the device that hosts the application goes down it does not stop the application from being hosted.  Finally if the application was to be expanded then it would only need to expand the server usage on Azure.

\subsection{Azure Virtual Machine}

\section{Container}
Containers are used when running software reliably on different types of environments. In this case it is changing from the test environment on our local computer to the production environment on the virtual machine.  This use of containers also allow to application to be run on other operating systems with ease.  The container platform used in this project is Docker.

\subsection{Docker}
