\section{Context}
\subsection{Angular}
Angular was initially released in September 2016, with its current stable release (11.2.9) released in April 2021.  Angular is a widely used framework for building single-page client applications using HTML and TypeScript.  With new releasing still being made to date is it a platform that is currently still in use in a wide range of applications, resulting in its use in this project.  The idea behind making a single-page client application was that they are in commonly used and offer a wide range of possibilities with regards to web development. \\

TypeScript is a programming language developed by Microsoft, is a strict syntactical super-set of JavaScript and adds optional static typing to the language.  Meaning that when Typscript is compiled it is converted to the specified version of JavaScript the programmer intends on using.  This results in existing JavaScript programs being valid TypeScript programs.  The importance of this is that JavaScript is one of the most use programming languages in web development.  With these characteristic, Angular is a platform that will mostly likely still be relevant and used for the foreseeable future and thus a valuable asset worth understanding.

\section{Project Objectives}
The primary goal of this project is to create an application to be use as tool to enhance the user experience of Tabletop RPGs(Role Playing Games).  This is done by the ability to share and store the relevant information through the creation of user Characters and Forums. While also providing the ability to communicate with other users, either by direct or group messaging.

\begin{itemize}
  \item Evaluate the needs of Tabetop RPGs players with regards to an application.
  \item Evaluate the current platforms for creating client applications.
  \item Build a database system for storage of the user information.
\end{itemize}

\section{Summary}
This section is comprised of brief descriptions of each chapter present in this disseration.

\subsection{Background}
In this chapter, a description of the various technologies used in the development of this project. These technologies include database tools, server-side Virtual Machine, application development framework, containerize software.
\subsection{Methodology}
\subsection{Design}
\subsection{Evaluation}
\subsection{Conclusion}
